\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/intro.tex
nit
intro minor edit

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, a new \mpc framework.
\tool is the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous work (up to a factor of 19x in our experiments, depending on the functionality) \nc{I added this but I guess we are saying it many times, but might be nice to highlight perf early no?}. Below we describe the
salient features of \tool.

@@

\subsubsection*{Cryptogaphic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and hence, the array accesses need not be compiled
obliviously. Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an effcient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Our evaluation
shows that the performance of these automatically generated protocols
is comparable
to or better than the custom, specialized protocols developed in previous works. Indeed, \tool is the first such cryptographic-cost
aware compiler.

@@

The rest of the paper is structured as follows. We formalize \tool and
prove its correctness and security theorems in
Section~\ref{sec:ld}. Section~\ref{sec:pipe} details our partitioning
scheme and proves its security. Section~\ref{sec:impl}
presents the implementation details, and
Section~\ref{sec:eval} present a comprehensive evaluation of \tool. We
begin with an overview of \tool through an example in Section~\ref{sec:ex}. \nc{provided a pointer to sec 2 as well.}

>>>>

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, a new \mpc framework.
\tool is the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous work %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.

@@

\subsubsection*{Cryptogaphic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and hence, the array accesses need not be compiled
obliviously. Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an effcient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Indeed, \tool is the
first such cryptographic-cost aware compiler.

@@

The rest of the paper is structured as follows. We formalize \tool and
prove its correctness and security theorems in
Section~\ref{sec:ld}. Section~\ref{sec:pipe} details our partitioning
scheme and proves its security. Section~\ref{sec:impl}
presents the implementation details, and
Section~\ref{sec:eval} present a comprehensive evaluation of \tool. We
begin with an overview of \tool through an example in
Section~\ref{sec:ex}. %\nc{provided a pointer to sec 2 as well.}
%\aseem{Sure :), I did not add it because Sec. 2 was just next line, so
%  I thought it did not need a pointer.}
